---
runtime: shiny
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---


```{r, message=FALSE,echo=FALSE,results='hide'}
library(knitr)
library(plotly)
library(ggplot2)
library(shiny)
library(mapproj)

```


# Introduction

Small usage example of the Dutch Geochemical Soil Atlas package. This document can be found at https://github.com/jspijker/dgsa-doc

The data of the atlas is part of the [DGSA package](https://github.com/jspijker/dgsa). Execute the following code to load it (using the devtools package):

```{r,echo=TRUE}
devtools::install_github("jspijker/dgsa")
library(dgsa)
data(atlas)
data(atlasmeta)

```

The DGSA package contains the data and 3 functions to visualise the data, these function are:
 * distribution
 * map
 * scatter
 
Documentation of these functions can be found in man pages. These functions give a ggplot2 object as result, see the ggplot2 library and man page.

# DGSA data and meta-data

Information how the data of the Dutch Geochemical Soil Atlas was obtained, please see the accompaniyng thesis of [Van Der Veer (2006)](https://dspace.library.uu.nl/handle/1874/13275).

The dataset is a single large data.frame named 'atlas' and a second data.frame with meta data named 'atlasmeta'. Please see the man pages of atlas and atlasmeta for more information

# Distribution

```{r echo = FALSE}

fluidRow(
  column(4,
         selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20)
         ),
column(4,
       sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
       ),
column(4,

       selectInput("var1_x",label="x as",
			                   choices=atlasmeta$label,selected="Al total")
       )
)

```

```{r echo = FALSE}
renderPlot({
  
  elem <-label2elem(input$var1_x)
  p <-distribution(elem,xadj=input$bw_adjust,xbin=input$n_breaks)
  p
  
})
```

# covariance

Interactive scatterplot showing covariance between two variables

```{r echo=FALSE}
fluidRow(
  column(6,
         selectInput("var2_x",label="x as",
			choices=atlasmeta$label,selected="Al total")
         ),
  column(6,
         
selectInput("var2_y",label="y as",
			choices=atlasmeta$label,selected="Zn total")
         )
)

```

```{r echo=FALSE, plotly=TRUE}
renderPlotly({

  elem.x <- label2elem(input$var2_x)
  elem.y <- label2elem(input$var2_y)
  
  p2 <- scatterplot(elem.x,elem.y)  
  p2
  
})
```

# maps

Bubble maps of top and subsoil

```{r echo=FALSE}

selectInput("var3_x",label="x as",
            	choices=atlasmeta$label,selected="Al total")
			

```

```{r echo=FALSE}

data(nlborder)
data(nlrivers)

nlshape <- nlborder
rivshape <- nlrivers

renderPlot({

  elem.x <- label2elem(input$var3_x)
  p <- map(elem.x)
  p
    
},width=900,height=600)
```




