---
title: "GeochemNL Leaflet"
author: "Job Spijker"
date: "6/12/2017"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)



```

This is a short example of how to use the dgsa package with R Leaflet

The atlas data in the dgsa package is an ordinary data.frame with a column with x-coordinates, and y-coordinates on a cartesian grid. The grid is the Dutch National Grid or [Amersfoort-RD](http://spatialreference.org/ref/epsg/amersfoort-rd-new/)

First we create a spatial points data frame to store our data, including the spatial projection. To keep things simple we use a subset of the total data.

```{r, echo=TRUE} 
library(leaflet)
library(sp)

devtools::install_github("dgsa","jspijker")
library(dgsa)

data(atlas)
data(atlasmeta)

# select data
atlas.sub<-subset(atlas,select=c("xrfal2o3","xrffe2o3","xrfni","xrfcu"))
atlas.coord<-subset(atlas,select=c("xcoord","ycoord"))

# add projection
atlas.sp<-SpatialPointsDataFrame(data=atlas.sub,coords = atlas.coord,
                                 proj4string = CRS("+proj=sterea +lat_0=52.15616055555555 +lon_0=5.38763888888889 +k=0.9999079 +x_0=155000 +y_0=463000 +ellps=bessel +units=m +no_defs "))

```

The Leaflet package expects all point, line, and shape data to be specified in latitude and longitude using
WGS 84 (a.k.a. EPSG:4326). By default, when displaying this data it projects everything to EPSG:3857 and
expects that any map tiles are also displayed in EPSG:3857.

So we reproject our data using spTransform

```{r, echo=TRUE}

atlas.osm<-spTransform(atlas.sp,CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))

```

No we create a simple map with markers

```{r,echo=TRUE}

m <- leaflet(data=atlas.osm) %>% addTiles %>% addMarkers

```

and plot the map:
```{r,echo=FALSE}
m
```
